\begin{thebibliography}{10}

% Chap01

% Chap02
\bibitem{chroot}
  \emph{MATTEO, Riondato. FreeBSD Handbook Chapter 15 Jails. freebsd.org. The FreeBSD Project.} [online]. 2014 [cit. 2019-04-21] Dostupné z: \url{https://www.freebsd.org/doc/en_US.ISO8859-1/books/handbook/jails.html}	
    
\bibitem{freebsd_jail}
    \emph{INDRASIRI, Kasun., P. SIRIWARDENA. Microservices for the Enterprise: Designing, Developing, and Deploying. Apress, 2018. ISBN 9781484238578.}

\bibitem{linux_vserver}
    \emph{Linux Vserver Overview. Linux Vserver.} [online]. 2006 [cit. 2019-04-21]. Dostupné z: \url{http://linux-vserver.org/Overview}
    
\bibitem{solaris_zones}
	\emph{BOTTOMLEY, James. Solaris Internals wiki:Zones.} [online]. 2007 [cit. 2019-04-21]. Dostupné z: \url{https://solarisinternals.com/wiki/index.php/Zones}	  
	
\bibitem{openvz}
    \emph{Openvz history. Openvz.} [online]. 2008 [cit. 2019-04-21]. Dostupné z: \url{https://wiki.openvz.org/History}
    
\bibitem{pc_cgroups}
    \emph{CORBET, Jonathan. Notes from a container.} [online]. 2007 [cit. 2019-04-21]. Dostupné z: \url{https://lwn.net/Articles/256389/}    

\bibitem{lxc}
    \emph{MARQUEZ, Ell. The History of Container Technology.} [online]. 2018 [cit. 2019-04-21]. Dostupné z: \url{https://linuxacademy.com/blog/containers/history-of-container-technology/}    

\bibitem{lmctfy}
    \emph{LMCTFY GitHub repozitář. GitHub.} [online]. 2016 [cit. 2019-04-21]. Dostupné z: \url{https://github.com/google/lmctfy/commit/0b317d7eb625d1877a8a0aaf2f46f770d9a5a50f}    

\bibitem{docker_rename}
	\emph{GLOUB, Ben. DotCloud, Inc. is Becoming Docker, Inc.} [online]. 2013 [cit. 2019-04-21]. Dostupné z: \url{https://blog.docker.com/2013/10/dotcloud-is-becoming-docker-inc/}
    
\bibitem{OCI_standard}
    \emph{POLVI, Alex. Making Sense of Container Standards and Foundations: OCI, CNCF, appc and rkt.} [online]. 2015 [cit. 2019-04-23]. Dostupné z: \url{https://coreos.com/blog/making-sense-of-standards.html} 

\bibitem{vm_container}
    \emph{GUO, Jianing. Demystifying container vs VM-based security: Security in plaintext.} [online]. 2017 [cit. 2019-04-23]. Dostupné z: \url{https://cloud.google.com/blog/products/gcp/demystifying-container-vs-vm-based-security-security-in-plaintext}

\bibitem{redhat_docker}
    \emph{ASAY, Matt. Why Red Hat makes more money on Docker than Docker does.} [online]. 2016 [2019-04-23]. Dostupné z: \url{https://www.techrepublic.com/article/why-red-hat-makes-more-money-on-docker-than-docker-does/}    

\bibitem{sysdig_survey}
    \emph{CARTER, Eric. 2018 Docker usage report.} [online]. 2018 [cit. 2019-05-02]. Dostupné z: \url{https://sysdig.com/blog/2018-docker-usage-report/}    

\bibitem{hq_survey}
    \emph{SHIMEL, Alan. ClusterHQ and DevOps.com survey show Containers poised for mass adoption.} [online]. 2015 [cit. 2019-05-02]. Dostupné z: \url{https://clusterhq.com/assets/pdfs/state-of-container-usage-june-2015.pdf}

\bibitem{unionfs}
    \emph{Docker OverlayFS Dokumentace. Docker.} [online]. 2016 [cit. 2019-05-02]. Dostupné z: \url{https://docs.docker.com/storage/storagedriver/overlayfs-driver/}  
    
\bibitem{docker_alpine}
    \emph{Alpine Linux - offical Image. Docker Hub.} [online]. 2019 [cit. 2019-05-05]. Dostupné z: \url{https://hub.docker.com/_/alpine}    
\bibitem{microservices1}
    \emph{ WOLFF, Eberhard. Microservices: Flexible Software Architectures.} [online]. 2016 [cit. 2019-05-03]. Dostupné z: \url{https://microservices.io/patterns/microservices.html}  

\bibitem{microservices2}
    \emph{RICHARDSON, Chris. Microservice architecture pattern.} [online]. 2017 [cit. 2019-05-03]. Dostupné z: \url{https://microservices.io/patterns/microservices.html}  

\bibitem{google_container}
    \emph{BEDA, Joe. Containers At Scale.} [online]. 2017 [cit. 2019-05-05]. Dostupné z: \url{https://speakerdeck.com/jbeda/containers-at-scale}

 \bibitem{swarm_compose}
    \emph{Deploy a stack to a swarm. Docker Doc.} [online]. 2019 [cit. 2019-05-05]. Dostupné z: \url{https://docs.docker.com/engine/swarm/stack-deploy/}  
 
 \bibitem{k8s_beda_commit}
    \emph{BEDA, Joe. First commit. Kubernetes GitHub.} [online]. 2014 [cit. 2019-05-05]. Dostupné z: \url{https://github.com/kubernetes/kubernetes/commit/2c4b3a562ce34cddc3f8218a2c4d11c7310e6d56}        	

\bibitem{k8s_docs_deployment}
    \emph{Deployments - Kubernetes. Kubernetes Docs.} [online]. 2019 [cit. 2019-05-14]. Dostupné z: \url{https://kubernetes.io/docs/concepts/workloads/controllers/deployment/} 
 
\bibitem{marathon}
	\emph{Marathon Docs. Mesos Sphere [online]. [cit. 2019-05-05]. Dostupné z: \url{https://mesosphere.github.io/marathon/}}
    
\bibitem{coreos_akvizice}
    \emph{Red Hat, Inc. Red Hat to Acquire CoreOS, Expanding its Kubernetes and Containers Leadership} [online]. 2018 [cit. 2019-05-05]. Dostupné z: \url{https://www.redhat.com/en/about/press-releases/red-hat-acquire-coreos-expanding-its-kubernetes-and-containers-leadership}  

\bibitem{cncf_survey}
    \emph{BARNARD, Kaitlyn. CNCF Survey: Use of Cloud Native Technologies in Production Has Grown Over 200\%.} [online]. 2018 [cit. 2019-05-22]. Dostupné z: \url{https://www.cncf.io/blog/2018/08/29/cncf-survey-use-of-cloud-native-technologies-in-production-has-grown-over-200-percent/}

\bibitem{k8s_DAM}
    \emph{Declarative application management in Kubernetes. Kubernetes GitHub.} [online]. 2019 [cit. 2019-05-05]. Dostupné z: \url{https://github.com/kubernetes/community/blob/master/contributors/design-proposals/architecture/declarative-application-management.md}

\bibitem{helm_deis}
    \emph{GUTHRIE, Scott. Microsoft to acquire Deis to help companies innovate with containers.} [online]. 2017 [cit. 2019-05-14]. Dostupné z: \url{https://blogs.microsoft.com/blog/2017/04/10/microsoft-acquire-deis-help-companies-innovate-containers/}

\bibitem{nginx_helm_template}
    \emph{Helm Nginx repository. Helm GitHub.} [online]. 2018 [cit. 2019-05-14]. Dostupné z: \url{https://github.com/helm/charts/tree/master/stable/nginx-ingress}        	
        	
\bibitem{helm_helm3}
    \emph{Helm 3 Design Proposal. Helm GitHub.} [online]. 2018 [cit. 2019-05-14]. Dostupné z: \url{https://github.com/helm/community/blob/master/helm-v3/000-helm-v3.md}
 	
\bibitem{kapitan_fleet}
    \emph{Kapitan templates for Kubernetes services. Richard Felkl GitHub.} [online]. 2019 [cit. 2019-05-20]. Dostupné z: \url{https://github.com/richardfelkl/kapitans-fleet}  

\bibitem{kustomize_sig}
    \emph{CLI Special Interest Group. Kubernetes GitHub.} [online]. 2019 [cit. 2019-05-14]. Dostupné z \url{https://github.com/kubernetes/community/tree/master/sig-cli}

\bibitem{kustomize_kubelet}
    \emph{Kubernetes SIG CLI. Kubernetes GitHub.} [online]. 2019 [cit. 2019-05-14]. Dostupné z: \url{https://github.com/kubernetes/community/tree/master/sig-cli}

\bibitem{kustomization_yaml}
    \emph{Kapitan templates for Kubernes services. Kubernetes GitHub.} [online]. 2018 [cit. 2019-05-20]. Dostupné z: \url{https://github.com/kubernetes-sigs/kustomize/blob/master/examples/wordpress/kustomization.yaml}  

\bibitem{operator_mongodb}
	\emph{ARJARAPU, Shyam. Getting started with MongoDB Enterprise Operator for Kubernetes.} [online]. 2018 [cit. 2019-05-20]. Dostupné z: \url{https://hackernoon.com/getting-started-with-mongodb-enterprise-operator-for-kubernetes-bb5d5205fe02}

% Chap03
\bibitem{legacy1}
    \emph{Migrating to Azure: transforming legacy applications into scalable cloud-first solutions. New York, NY: Springer Science+Business Media, 2018. ISBN 9781484235843.} 

\bibitem{legacy2}
    \emph{WOOTTON, Benjamin. What Are Legacy Systems and What Should You Do with Them?} [online]. 2017 [cit. 2019-05-24]. Dostupné z: \url{https://www.contino.io/insights/what-are-legacy-systems-and-what-should-you-do-with-them} 
    
\bibitem{NASA_legacy}
    \emph{ORREGO S., MUNDY, E. Andres, Gregory.  A study of software reuse in NASA legacy systems.} [online]. 2007, ISSE. 3. 167-180. 10.1007/s11334-007-0027-y.[cit. 2019-5-5]

\bibitem{agilni_manifest}
    \emph{BECK, K., BEEDLE, M., van BENNEKUM, A., COCKBURN, A., CUNNINGHAM, W., FOWLER, M., Grenning, J., Highsmith, J., Hunt, A., JEFFRIES, R., KERN, J., MARICK, B., MARTIN, R. C., MELLOR, S., SCHWABER, K., SUTHERLAND, J. a THOMAS, D. (2001). Manifesto for Agile Software Development Manifesto for Agile Software Development.} 

\bibitem{legacy_testing}
    \emph{MALLADI, Srinivas. G. RAMAKRISHNA. a R RAJASEKHARA a E. Babu. Analysis of Legacy System in Software Application Development: A Comparative Survey. 2016. International Journal of Electrical and Computer Engineering (IJECE). 6. 292-297. 10.11591/ijece.v6i1.8367.}


\bibitem{squad_framework}
    \emph{FERNANDES, Thaisa. Spotify Squad framework — Part I} [online]. 2017 [cit. 2019-05-24]. Dostupné z: \url{https://medium.com/productmanagement101/spotify-squad-framework-part-i-8f74bcfcd761} 

\bibitem{legacy_testy}
    \emph{KESSLER, David. Automated Testing Strategy for Legacy Systems.} [online]. 2012 [cit. 2019-06-01]. Dostupné z: \url{https://www.sourceallies.com/2012/04/automated-testing-strategies-for-legacy-systems/} 
 
\bibitem{legacy_years}
    \emph{LAMB, John. Legacy systems continue to have a place in the enterprise.} [online]. 2008 [cit. 2019-06-01]. Dostupné z: \url{https://www.computerweekly.com/feature/Legacy-systems-continue-to-have-a-place-in-the-enterprise} 
    
\bibitem{cicd_fullauto}
    \emph{AZERI, Izzy. What Is CI/CD?} [online]. 2017 [cit. 2019-06-02]. Dostupné z: \url{https://dzone.com/articles/what-is-cicd} 

% Chap04
\bibitem{nasa_nova}
    \emph{RYAN, Paul. NASA and Rackspace part the clouds with open source project.} [online]. 2010 [cit. 2019-06-10]. Dostupné z: \url{https://arstechnica.com/information-technology/2010/07/nasa-and-rackspace-part-the-clouds-with-open-source-project/} 

\bibitem{github_pipelib}
    \emph{Mirantis/pipeline-library repozitář. GitHub.} [online]. 2017 [cit. 2019-06-10]. Dostupné z: \url{https://github.com/Mirantis/pipeline-library/} 

\bibitem{github_mkpipelines}
    \emph{Mirantis/mk-pipeline repozitář. GitHub.} [online]. 2017 [cit. 2019-06-10]. Dostupné z: \url{https://github.com/Mirantis/mk-pipelines} 
    
\bibitem{mcp_arch_comp}
    \emph{Mirantis Dokumentace: OpenStack compact cloud architecture. Mirantis Doc.} [online]. 2018 [cit. 2019-06-10]. Dostupné z: \url{https://docs.mirantis.com/mcp/q4-18/mcp-standard-configuration/os-scaling/os-compact-cloud-arch.html}  

\bibitem{mcp_gerrit}
    \emph{MCP Gerrit Review page. Mirantis Gerrit.} [online]. 2017 [cit. 2019-06-11]. Dostupné z: \url{https://gerrit.mcp.mirantis.com/}

\bibitem{day01_image}
    \emph{Mirantis Dokumentace: Deploy salt master node. Mirantis Docs team.} [online]. 2019 [cit. 2019-06-11]. Dostupné z: \url{https://docs.mirantis.com/mcp/q4-18/mcp-deployment-guide/deploy-mcp-drivetrain/deploy-salt-master-node.html} 

\bibitem{github_model}
    \emph{MCP Reclass system model. Mirantis GitHub.} [online]. 2016 [cit. 2019-06-12]. Dostupné z: \url{https://github.com/Mirantis/reclass-system-salt-model}

\bibitem{cookiecutter}
    \emph{Cookiecutter Repository. Cookiecutter GitHub.} [online]. 2016 [cit. 2019-06-12]. Dostupné z: \url{https://github.com/audreyr/cookiecutter}


% Chap05
\bibitem{kolla_ansible}
    \emph{Kolla dokumentace. OpenStack.} [online]. 2016 [cit. 2019-06-24]. Dostupné z: \url{https://docs.openstack.org/kolla-ansible/latest/}
    
\bibitem{airship}
    \emph{Whitepaper - A New Open Infrastructure Project for OpenStack. AT\&T Cloud Platform Development team.} [online]. 2018 [cit. 2019-06-24]. Dostupné z: \url{https://about.att.com/ecms/dam/inside_connections_blogdocs/Whitepaper\%20-\%20Airship\%20a\%20New\%20Open\%20Infrastructure\%20Project\%20for\%20OpenStack\%20v1.0.pdf}

\bibitem{k8s_devs}
    \emph{HECK, Joseph. Kubernetes for Developers. Packt Pub, 2018. ISBN 9781788834759.}
    	
\bibitem{nova_scale}
    \emph{BELOVA, Dina, A. SHAPOSHNIKOV a M. SIMONIN. Chasing 1000 nodes scale.} [online]. 2016 [cit. 2019-06-24]. Dostupné z: \url{https://www.openstack.org/assets/presentation-media/Chasing-1000-nodes-scale.pdf}

% Chap06
\bibitem{envboot_dep}
    \emph{OpenStack Bootstrapping Identity. OpenStack.} [online]. 2019 [cit. 2019-07-04]. Dostupné z: \url{https://docs.openstack.org/keystone/queens/admin/identity-bootstrap.html}

\bibitem{okd_gettingstarted}
    \emph{Getting started with the Operator SDK. OKD docs.} [online]. 2019 [cit. 2019-07-05]. Dostupné z: \url{https://docs.okd.io/latest/operators/osdk-getting-started.html}

\bibitem{gh_openstack_images}
    \emph{LotharKAtt/openstack-images repozitář. GitHub.} [online]. 2019 [cit. 2019-07-09]. Dostupné z: \url{https://github.com/LotharKAtt/openstack-images}

\bibitem{docker_docs}
    \emph{Docker Create a base image. Docker docs.} [online]. 2019 [cit. 2019-07-10]. Dostupné z: \url{https://docs.docker.com/develop/develop-images/baseimages/}

\bibitem{mirantis_releasemap}
    \emph{MCP Release Support Status. Mirantis.} [online]. 2019 [cit. 2019-07-10]. Dostupné z: \url{https://www.mirantis.com/software/openstack/releases/}

\bibitem{keystone-admin-dep}
    \emph{OpenStack Rocky Series Release Notes. OpenStack.} [online]. 2019 [cit. 2019-07-11]. Dostupné z: \url{https://docs.openstack.org/releasenotes/puppet-keystone/rocky.html}
    
\bibitem{repo_openstack_operator}
    \emph{LotharKAtt/openstack-operátor repozitář. GitHub.} [online]. 2019 [cit. 2019-07-11]. Dostupné z: \url{https://github.com/LotharKAtt/openstack-operator}


\bibitem{mastering_k8s}
    \emph{SAYFAN, Gigi. Mastering Kubernetes. Packt Pub, 2017. ISBN 9781786461001.}

\bibitem{gophercloud}
    \emph{Gophercloud package dokumentace. Golang Docs.} [online]. 2019 [cit. 2019-07-15]. Dostupné z: \url{https://godoc.org/github.com/gophercloud/gophercloud}
% Chap07

% Chap08
\end{thebibliography}
